\documentclass{resume}

\begin{document}

\namesection{Emma Spinale}{
    781.697.4381\\
  \href{mailto:emma.spinale@richmond.edu}{emma.spinale@richmond.edu}

\bigskip
}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE// TEST 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of}
\subsection{Richmond}
\descript{Bachelor of Science}
\descript{Math/Computer Science}
\location{Expected May 2021 | Richmond, VA}
\location{Overall GPA: 3.9}
Dean's List\\
Phi Eta Sigma Honors \\
{\descript{Selected Courses}}
Multivariate Calculus\\
Probability Theory \\
Linear Algebra \\
Abstract Math\\
Simulation in R\\
Data Structures\\
Discrete Structures\\
Algorithms\\
\metanote{(Completed by Summer 2020)}
Software Systems Development\\
Computer Organization\\
Abstract Algebra\\
Real Analysis\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Languages}
Python \\
Java\\
SQL\\
R\\
TeX \\
JavaScript\\
HTML/CSS\\
Shell\\

% \medskip

% \subsection{Skills}
% Algorithms\\
% Databse Design and Implementation\\
% Data Structures\\
% Data Visualization

% \section{Interests}
% Hiking\\
% Travel\\
% Foodie\\
% Ceramics\\
% Reading\\


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS/CONTACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Contact}
\begin{tabular}{cl}
  \color{subheadings}\selectfont\faLinkedin & \href{https://www.linkedin.com/emmaspinale}{linkedin.com/emmaspinale} \\
  \color{subheadings}\selectfont\faEnvelope & \href{mailto:emma.spinale@richmond.edu}{emma.spinale@richmond.edu} \\
  \color{subheadings}\selectfont\faPhone & 781.697.4381 \\
  \color{subheadings}\selectfont\faMapMarker & 62 Northgate Rd \\
  \phantom{\color{subheadings}\selectfont\faMapMarker} & Wellesley, MA 02481 \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{The MITRE Corporation}
\descript{| Cybersecurity Software Engineering Intern}
\location{May - August 2019 | Bedford, MA}
\vspace{1.25\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Created a secure, scalable, internal self-service platform for data ETL, storage, analytics, and exploitation
\item Constructed the data ingest process and designed an advanced schema in MySQL through Amazon RDS
\item Collaborated with a small team using agile software development methods to promote responsibility and accountability
\end{tightemize}
\sectionsep

\runsubsection{University of Richmond}
\descript{| Writing Consultant }
\location{Winter 2018 - Present | Richmond, VA}
%\vspace{1.25\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Spend 8-10 hours weekly meeting with students, editing essays, and providing feedback. 
\item Selected via appointment by english faculty due to excellence in academic writing.
\item Completed 40 hour intensive training course to refine editing  and communication skills.
\end{tightemize}
\sectionsep

\runsubsection{University of Richmond Mathematics Department}
\descript{| Undergraduate Research Team Member}
\location{Fall 2018 - Spring 2019 | Richmond, VA}
\begin{tightemize}
\item Worked with a small team of students and faculty to create further breakthroughs in the field of coding theory.
\item Identified and develop strategies to reduce errors in long-distance communication signals.
\end{tightemize}
\sectionsep


\runsubsection{Tenacre Country Day School}
\descript{| Counselor }
\location{Summer 2017-2018 | Wellesley, MA}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Managed a team of counselors to ensure the safety of 30+ 3 and 4 year old children.
\item Communicated scheduling decisions to camp management and parents regarding the well being of the campers. 
\end{tightemize}
\sectionsep

% \runsubsection{Gap, Inc}
% \descript{| Sales Associate }
% \location{Winter 2015 - Spring 2017 | Wellesley, MA}
% \begin{tightemize}
% \item Tasked with building brand loyalty by working with consumers, designing loyalty programs, and scheduling promotions.
% \item Designed window displays and set the store layout to reflect the Gap's integrated marketing objectives. 
% \end{tightemize}
% \sectionsep

\section{Leadership \& Activities}

\runsubsection{Spiders Against Sexual Assault and Violence}
\descript{| Member}
\location{Fall 2017 - Present | Richmond, VA}
\begin{tightemize}
\item Work closely with administration to raise awareness of and propose solutions to the issue of sexual assault on college campuses.
\item Successfully lobbied administration to expand their sexual assault resources on campus.
\item Worked with Title IX coordinators to develop training and workshops for students and faculty to address issues around sexual violence.
\end{tightemize}
\sectionsep

%\runsubsection{Pine Street Inn}
%\descript{| Volunteer}
%\location{Monthly, 2010 – Present | Dorchester, MA}
%\begin{tightemize}
%\item Volunteer at a homeless shelter that provides women a transitional home during turbulent life events.
%\item Tasked with the care of several women during their stay providing professional advice to assist in recovery. 
%\end{tightemize}
%\sectionsep

% \runsubsection{Red Cross Club}
% \descript{| Founder and Member}
% \location{2014 - 2017 | Boston, MA}
% \begin{tightemize}
% \item Created a local branch of the Red Cross Club and accumulated over 30 members. 
% \item Organized and ran events and fundraisers in association with the national Red Cross, raising over \$1000 and helping to sponsor several blood drives on my high school campus. 
% \end{tightemize}
% \sectionsep






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}
\end{document}
